Unbalanced Mallows Models for Optimizing Expensive Black-Box Permutation Problems

### 2021-01-20 paper/main.tex
Reviewer comments.

\subsubsection{Learning step}
%
At each iteration, we start by fitting a MM to the sample $S$, which implies
estimating $\hat\sigma_0$ and $\theta$. Parameter $\theta$ is updated
deterministically at the sampling step.  The parameter $\sigma_0$, however, is
learned from the current sample $S$ by using the uBorda algorithm with a weight
$w(\sigma)=\rho^{f(\sigma)}$ (Section~\ref{sec:uborda}). The learning rate is
controlled by parameter $\rho \in (0,1)$. %
In UMM, the value of $\rho$ depends on the set of true fitness evaluations $F$
and it is set at each iteration such that the largest $100r_1$\% of the mass of
the weights is concentrated in the best $100r_2$\% of the solutions in $S$, i.e.,
%
\begin{equation}
  \begin{split}
  r_1 \sum_{\sigma\in S}\rho^{f(\sigma)} =  \sum_{\sigma'\in S'}\rho^{f(\sigma')} \quad\text{where}\; &|S'| = r_2|S| \\[-1.2em]
  &\land \forall \sigma'\in S', \sigma\in S\setminus S' : f(\sigma')\leq f(\sigma).
  \end{split}
\end{equation}
%
i.e., $S'$ contains the $r_2|S|$ elements of $S$ with the best corresponding fitness values in $F$. %The values of $r_1, r_2 \in (0, 1)$ are user-defined and control the balance between exploration and intensification. %: extreme different values bias the sampling towards the best solutions found so far, which may lead to quick stagnation, whereas values (0.5,0.5) make the sampling more uniform, thus slowing down the learning.

@@

Parameter $\theta$ is set automatically by the algorithm to control the diversification and intensification trade off. At the first iteration, $\theta$ is set so that  $\Edist = \binom{n}{4}$ (half of the expected distance for the uniform distribution), and then the expected distance linearly decreases until the last iteration where $\theta$ is set such that $\Edist = 1$. Despite it is not possible to isolate $\theta$ in Eq.~\eqref{eq:expectation}, its monotonicity allows the use of bisection methods for efficiently finding an approximation.

@@

To avoid sampling the same points more than once and increase the exploration of the search space, the algorithm samples $\beta$ permutations, $\Sigma$. Then it selects  for evaluation the farthest from permutations already evaluated ($S$), as shown in line~\ref{line:distance} of Algorithm~\ref{alg:umm}.
%i.e.,  $\sigma\in \Sigma$ such that $\sigma = \argmax_{\sigma'\in \Sigma}\min d(\sigma', \pi)$ for every $\pi\in S$.

>>>>

\subsubsection{Learning step}
%
At each iteration, we start by fitting a MM to the sample $S$, which implies
estimating $\hat\sigma_0$ and $\theta$. Parameter $\theta$ is updated
deterministically at the sampling step.  The parameter $\sigma_0$, however, is
learned from the current sample $S$ by using the uBorda algorithm with a weight
$w(\sigma)=\rho^{f(\sigma)}$ (Section~\ref{sec:uborda}). The learning rate is
controlled by parameter $\rho \in (0,1)$. %
In UMM, the value of $\rho$ depends on the set of true fitness evaluations $F$
and it is set at each iteration such that the largest $100r_1$\% of the mass of
the weights is concentrated in the best $100r_2$\% of the solutions in $S$, i.e.,\MANUEL{Reviewer 3:  Justify the form of the formula used to learn the "learning rate" $\rho$ (equation 4). Why this particular approach was chosen?}
%
\begin{equation}
  \begin{split}
  r_1 \sum_{\sigma\in S}\rho^{f(\sigma)} =  \sum_{\sigma'\in S'}\rho^{f(\sigma')} \quad\text{where}\; &|S'| = r_2|S| \\[-1.2em]
  &\land \forall \sigma'\in S', \sigma\in S\setminus S' : f(\sigma')\leq f(\sigma).
  \end{split}
\end{equation}
%
i.e., $S'$ contains the $r_2|S|$ elements of $S$ with the best corresponding fitness values in $F$. %The values of $r_1, r_2 \in (0, 1)$ are user-defined and control the balance between exploration and intensification. %: extreme different values bias the sampling towards the best solutions found so far, which may lead to quick stagnation, whereas values (0.5,0.5) make the sampling more uniform, thus slowing down the learning.

@@

Parameter $\theta$ is set automatically by the algorithm to control the diversification and intensification trade off. At the first iteration, $\theta$ is set so that  $\Edist = \binom{n}{4}$ (half of the expected distance for the uniform distribution),\MANUEL{Reviewer 3: "At the first iteration, $\theta$ is set so that $E[D] = {n \choose 4}$". Why?} and then the expected distance linearly decreases until the last iteration where $\theta$ is set such that $\Edist = 1$. Despite it is not possible to isolate $\theta$ in Eq.~\eqref{eq:expectation}, its monotonicity allows the use of bisection methods for efficiently finding an approximation.

@@

To increase the exploration of the search space, the algorithm samples $\beta$ permutations, $\Sigma$. Then it selects  for evaluation the farthest from permutations already evaluated ($S$), as shown in line~\ref{line:distance} of Algorithm~\ref{alg:umm}.
%i.e.,  $\sigma\in \Sigma$ such that $\sigma = \argmax_{\sigma'\in \Sigma}\min d(\sigma', \pi)$ for every $\pi\in S$.
